Hypertension and microbiome

### 2019-05-15 articletwo.Rmd
More salt models

@@

@@

pcoa.df %>% pull(STATETREATMENT)

@@

@@

@@

@@

adjmean.lacto.saltgroup <- predict(lm.lacto.saltgroup,
                               df.genus.salt.unadjusted,
                               interval = "confidence") %>%
    as.data.frame %>%
    dplyr::rename(estimate = fit,
                  conf.low = lwr,
                  conf.high = upr) %>%
    tibble::rownames_to_column("term")
```

@@

```{r glm htn lacto}
glm.hypertension.lactogroup <- glm(HYPERTENSION ~ lacto_groups + BL_AGE + SEX,
                  family = binomial(link=logit),
                  data = df.genus.salt) %>%
    broom::tidy(conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE)
glm.hypertension.lactogroup %>% kable
```

>>>>

```{r check adonis, eval = FALSE}
ad.min <- adonis(bray.dist.m.species ~ DIASM + BL_AGE + SEX,
             data = meta(pseq.species),
             permutations = 100)

ad.max <- adonis(bray.dist.m.species ~ DIASM + BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB +
                     BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09,
             data = meta(pseq.species),
             permutations = 1000)

```

@@

```{r difference in beta diversity}
merge(diversities$min %>% select(response, R2),
      diversities$max %>% select(response, R2), by = "response") %>%
    mutate(R2.diff = R2.y - R2.x) %>%
    kable
```

@@

@@

maas.results.df.signf %>% pull(Feature) %>% sort %>% unique %>% paste(., collapse=", ")

@@

Characteristics in salt analysis

```{r salt characteristics}

pseq.genus.salt %>%
    meta %>%
    gather(key,value) %>%
    group_by(key) %>%
    summarise_all(funs(N = n(),
                       Mean = mean(as.numeric(value), na.rm = TRUE),
                       sd = sd(as.numeric(value), na.rm = TRUE),
                       NAs = sum(is.na(value))))  %>%
    kable()

```

@@

```{r equal variance}
bartlett.test(lactobacillus.bacteria ~ salt_groups, data = df.genus.salt)
```

```{r one way test salt groups}
oneway.test(lactobacillus.bacteria ~ salt_groups, data = df.genus.salt, var.equal = TRUE)
```

@@

adjmean.lacto.saltgroup <- predict(lm.lacto.saltgroup,
                               df.genus.salt.unadjusted,
                               interval = "confidence") %>%
    as.data.frame %>%
    dplyr::rename(estimate = fit,
                  conf.low = lwr,
                  conf.high = upr) %>%
    rownames::tibble_to_column("term")
```

@@

```{r glm htn lacto groups}
glm.hypertension.lactogroup <- glm(HYPERTENSION ~ lacto_groups + BL_AGE + SEX,
                  family = binomial(link=logit),
                  data = df.genus.salt) %>%
    broom::tidy(conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE)
glm.hypertension.lactogroup %>% kable
```

```{r glm htn lacto continuous}
glm.hypertension.lactocontinuous <- glm(HYPERTENSION ~ lactobacillus.bacteria + BL_AGE + SEX,
                  family = binomial(link=logit),
                  data = df.genus.salt) %>%
    broom::tidy(conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE)
glm.hypertension.lactocontinuous %>% kable
```

Daily urine sodium and BP

```{r dUNA RR}
calculateglm(df.genus.salt, modelstring = "%s ~ dUNA + BL_AGE + SEX", filterstr = "dUNA") %>%
    select(response, term, estimate, p.value) %>%
    kable
```

Daily urine sodium and BP

```{r lactobacillus RR}
calculateglm(df.genus.salt,
             modelstring = "%s ~ lactobacillus.bacteria + BL_AGE + SEX",
             filterstr = "lactobacillus") %>%
    select(response, term, estimate, p.value) %>%
    kable
```

Assesment for linear model asumptions

```{r table map lactobacillus}
gvlma.table.plot(lm(log(MAP) ~ lactobacillus.bacteria + BL_AGE + SEX, data = df.genus.salt))$table %>% kable
```

```{r plot map lactobacillus, fig.width=12, fig.height=14}
gvlma.table.plot(lm(MAP ~ lactobacillus.bacteria + BL_AGE + SEX, data = df.genus.salt))$plot %>% plot
```
